---
title: "pa3"
author: "Joselyn Rodriguez"
date: "2/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load}
library(tidyverse)
library(languageR)
```

```{r options}
data(package = "languageR")
```

1. Load the dataset of your choice and get information about its structure (remember all code needs to be inside a knitr code chunk).

```{r}
# dataset of choice? etymology: Etymological age and regularity in Dutch
ety <- languageR::etymology # already tidied
View(ety)

# another option
# dv <- languageR::finalDevoicing
# View(dv)
```

2. Tidy the dataset (every variable gets a column, every observation occupies a single row), if necessary.

Already tidied.

3. Calculate descriptive statistics of your choice.

```{r}
summary(ety)
```

4. Select two continuous variables and fit a model to the data (bivariate regression).

```{r model}
# make a model
model <- lm(WrittenFrequency ~ NcountStem, data = ety)
summary(model)
```


5. Generate a plot that includes a regression line.

```{r plot}
plot <- ggplot(data = ety, aes(x = WrittenFrequency, y = NcountStem)) +
            geom_jitter() +
            geom_smooth(method = "lm", se =  TRUE)
          
plot
```


6. Write up some general observations (1-2 paragraphs max)

It looks like there is actually a positive relationship between the written frequency of a word in Dutch and how many orthographic neighbors the word has. This makes sense as the more frequent a word is, the more likely it is to have other words that are similar orthographically as it's getting shorter and shorter words are also probably more alike in general.




